Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India

### 2018-01-24 inst/doc/draft2.Rmd
Uppangala 0.1.9041 January 2018 Tabebuia 2nd run

```{r GWMH1a}
GWM <- L %>% 
  t() %>% 
  data.frame() %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  group_by(strata, community) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# nQ <- array(rep(as.matrix(Q), n),
#             c(dim(Q), n),
#             list(row.names(Q), names(Q), 1:n))
# nQ <- array(apply(nQ, 3, function(x){
#   x[,'strata'] <- sample(x[,'strata'])
#   return(x)}), c(dim(Q), n),
#   list(row.names(Q), names(Q), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('L', 'nQ'))
# nGWM <- parApply(cl, nQ, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   L %>%
#     t() %>%
#     data.frame() %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(data.frame(x)) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     group_by(strata, community) %>%
#     mutate_each(funs(as.character), -abundance) %>%
#     mutate_each(funs(as.numeric), -abundance) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# })
# stopCluster(cl)
# nGWM <- array(unlist(lapply(nGWM, function(x) as.matrix(x[3:9]))),
#               c(dim(GWM[3:9]), n),
#               list(row.names(GWM), names(GWM[3:9]), 1:n))
# GWM_ses <- GWM
# GWM_ses[3:9] <- (GWM[3:9] - apply(nGWM, 1:2, mean, na.rm = T))/apply(nGWM, 1:2, sd, na.rm = T)
# rm(cl, nQ, nGWM)
# save(GWM_ses, file = file.path(path, 'GWM_NM1_ses.Rdata'))
load(file.path(path, 'GWM_NM1_ses.Rdata'))
GWM_ses %>% 
  select(-community, -LES, -WES) %>% 
  group_by(strata) %>% 
  mutate_all(function(x) abs(x) > 0.95) %>% 
  summarise_all(function(x) sum(x, na.rm = T)/length(x)*100) %>% 
  kable(caption = 'Percentage of community significantly (p-value<0.05) different from null expectations with null model NM1 for each trait of GWMs, for canopy (C) and understorey (U) guilds, in abundance. See table \\@ref(tab:Traits) for abbreviations.')
```

@@

```{r GWVH1b}
GWV <- L %>% 
  t() %>% 
  data.frame() %>% 
  filter(sum(.) > 2) %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  melt(id.vars = c('strata', 'community', 'abundance'),
       variable.name = 'trait', value.name = 'trait_value') %>% 
  left_join(melt(GWM, id.vars = c('strata', 'community'),
                 variable.name = 'trait', value.name = 'GWM')) %>% 
  group_by(strata, community, trait) %>% 
  mutate(GWV = (trait_value - GWM)^2) %>% 
  select(-trait_value, -GWM) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  dcast(strata + community ~ trait)
# nL <- array(replicate(n, t(apply(L, 1, function(x){
#   x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0])
#   x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0])
#   return(x)
#   }))), c(dim(L), n), list(row.names(L), names(L), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('nL', 'Q', 'GWM'))
# nGWV <- parApply(cl, nL, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   x %>%
#     t() %>%
#     data.frame() %>%
#     filter(sum(.) > 2) %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(Q) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     melt(id.vars = c('strata', 'community', 'abundance'),
#          variable.name = 'trait', value.name = 'trait_value') %>%
#     left_join(melt(GWM, id.vars = c('strata', 'community'),
#                    variable.name = 'trait', value.name = 'GWM')) %>%
#     group_by(strata, community, trait) %>%
#     mutate(GWV = (trait_value - GWM)^2) %>%
#     select(-trait_value, -GWM) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>%
#     dcast(strata + community ~ trait)
# })
# stopCluster(cl)
# nGWV <- array(unlist(lapply(nGWV, function(x) as.matrix(x[3:9]))),
#               c(dim(GWV[3:9]), n),
#               list(row.names(GWV), names(GWV[3:9]), 1:n))
# GWV_ses <- GWV
# GWV_ses[3:9] <- (GWV[3:9] - apply(nGWV, 1:2, mean, na.rm = T))/apply(nGWV, 1:2, sd, na.rm = T)
# rm(cl, nL, nGWV)
# save(GWV_ses, file = file.path(path, 'GWV_NM3_ses.Rdata'))
load(file.path(path, 'GWV_NM3_ses.Rdata'))
GWV_ses %>% 
  select(-community, -LES, -WES) %>% 
  group_by(strata) %>% 
  mutate_all(function(x) abs(x) > 0.95) %>% 
  summarise_all(function(x) sum(x, na.rm = T)/length(x)*100) %>% 
  kable(caption = 'Percentage of community significantly (p-value<0.05) different from null expectations with null model NM3 for each trait of GWVs, for canopy (C) and understorey (U) guilds, in abundance. See table \\@ref(tab:Traits) for abbreviations.')
```

@@

```{r GWMH2a}
GWM <- L %>% 
  t() %>% 
  data.frame() %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  group_by(strata, community) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# nQ <- array(rep(as.matrix(Q), n),
#             c(dim(Q), n),
#             list(row.names(Q), names(Q), 1:n))
# nQ <- array(apply(nQ, 3, function(x){
#   x[which(x[,"strata"] == "C"),'SpCode'] <- sample(x[which(x[,"strata"] == "C"),'SpCode'])
#   x[which(x[,"strata"] == "U"),'SpCode'] <- sample(x[which(x[,"strata"] == "U"),'SpCode'])
#   return(x)
#   }), c(dim(Q), n), list(row.names(Q), names(Q), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('L', 'nQ'))
# nGWM <- parApply(cl, nQ, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   L %>%
#     t() %>%
#     data.frame() %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(data.frame(x)) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     group_by(strata, community) %>%
#     mutate_each(funs(as.character), -abundance) %>%
#     mutate_each(funs(as.numeric), -abundance) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# })
# stopCluster(cl)
# nGWM <- array(unlist(lapply(nGWM, function(x) as.matrix(x[3:9]))),
#               c(dim(GWM[3:9]), n),
#               list(row.names(GWM), names(GWM[3:9]), 1:n))
# GWM_ses <- GWM
# GWM_ses[3:9] <- (GWM[3:9] - apply(nGWM, 1:2, mean, na.rm = T))/apply(nGWM, 1:2, sd, na.rm = T)
# rm(cl, nQ, nGWM)
# save(GWM_ses, file = file.path(path, 'GWM_NM2_ses.Rdata'))
load(file.path(path, 'GWM_NM2_ses.Rdata'))
GWM_ses %>% 
  melt(id.vars = c('strata', 'community')) %>% 
  rename(trait = variable) %>% 
  rename(SES = value) %>% 
  left_join(R) %>%
  select(-community) %>% 
  group_by(strata, trait) %>% 
  do(tidy(step(lm(SES ~ Slope + Curvature + Wetness + SW + Canopy + BA, .), 
          direction = 'both', trace = 0))) %>% 
  group_by(strata, trait, term) %>%
  transmute(value = paste(format(estimate, scientific = T, digits = 2, trim = T), 
                          stars(p.value, ns = '   '))) %>% 
  dcast(strata + trait ~ term) %>% 
  select(strata, trait, Slope, Curvature, Wetness, SW, Canopy, BA) %>% 
  mutate_each(funs(replace(., is.na(.), ' '))) %>% 
  filter(trait != 'LES') %>% 
  filter(trait != 'WES') %>%
  bold() %>% 
  kable(caption = 'Linear models of the standardized effect size (SES) with null model NM2 for each trait of GWMs, for canopy (C) and understorey (U) guilds, in abundance. We performed stepwise selection of the predictors including slope, curvature, wetness southwesterness (SW), canopy height (Canopy) and basal area (BA), and only the selected predictors are shown. See table \\@ref(tab:Traits) for abbreviations. Bold and number of asterisk indicates the significance threshold ( * p-value<0.05, ** p-value <0.01, *** p-value<0.001).')
```

@@

```{r GWVH2b}
GWV <- L %>% 
  t() %>% 
  data.frame() %>% 
  filter(sum(.) > 2) %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  melt(id.vars = c('strata', 'community', 'abundance'),
       variable.name = 'trait', value.name = 'trait_value') %>% 
  left_join(melt(GWM, id.vars = c('strata', 'community'),
                 variable.name = 'trait', value.name = 'GWM')) %>% 
  group_by(strata, community, trait) %>% 
  mutate(GWV = (trait_value - GWM)^2) %>% 
  select(-trait_value, -GWM) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  dcast(strata + community ~ trait)
# nL <- array(replicate(n, t(apply(L, 1, function(x){
#   x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0])
#   x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0])
#   return(x)
#   }))), c(dim(L), n), list(row.names(L), names(L), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('nL', 'Q', 'GWM'))
# nGWV <- parApply(cl, nL, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   x %>%
#     t() %>%
#     data.frame() %>%
#     filter(sum(.) > 2) %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(Q) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     melt(id.vars = c('strata', 'community', 'abundance'),
#          variable.name = 'trait', value.name = 'trait_value') %>%
#     left_join(melt(GWM, id.vars = c('strata', 'community'),
#                    variable.name = 'trait', value.name = 'GWM')) %>%
#     group_by(strata, community, trait) %>%
#     mutate(GWV = (trait_value - GWM)^2) %>%
#     select(-trait_value, -GWM) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>%
#     dcast(strata + community ~ trait)
# })
# stopCluster(cl)
# nGWV <- array(unlist(lapply(nGWV, function(x) as.matrix(x[3:9]))),
#               c(dim(GWV[3:9]), n),
#               list(row.names(GWV), names(GWV[3:9]), 1:n))
# GWV_ses <- GWV
# GWV_ses[3:9] <- (GWV[3:9] - apply(nGWV, 1:2, mean, na.rm = T))/apply(nGWV, 1:2, sd, na.rm = T)
# rm(cl, nL, nGWV)
# save(GWV_ses, file = file.path(path, 'GWV_NM3_ses.Rdata'))
load(file.path(path, 'GWV_NM3_ses.Rdata'))
GWV_ses %>% 
  melt(id.vars = c('strata', 'community')) %>% 
  rename(trait = variable) %>% 
  rename(SES = value) %>% 
  left_join(R) %>%
  select(-community) %>% 
  group_by(strata, trait) %>% 
  do(tidy(step(lm(SES ~ Slope + Curvature + Wetness + SW + Canopy + BA, .), 
          direction = 'both', trace = 0))) %>% 
  group_by(strata, trait, term) %>%
  transmute(value = paste(format(estimate, scientific = T, digits = 2, trim = T), 
                          stars(p.value, ns = '   '))) %>% 
  dcast(strata + trait ~ term) %>% 
  {if(!("Slope" %in% names(.))) mutate(., Slope = NA)} %>% 
  select(strata, trait, Slope, Curvature, Wetness, SW, Canopy, BA) %>% 
  mutate_each(funs(replace(., is.na(.), ' '))) %>% 
  filter(trait != 'LES') %>% 
  filter(trait != 'WES') %>%
  bold() %>% 
  kable(caption = 'Linear models of the standardized effect sizes (SES) with null model NM3 of GWV for canopy (C) and understorey (U) guilds. We performed stepwise selection of the predictors including slope, curvature, wetness southwesterness (SW), canopy height (Canopy) and basal area (BA), and only the selected predictors are shown. See table \\@ref(tab:Traits) for abbreviations. Bold and  number of asterisk indicates the significance threshold ( * p-value<0.05, ** p-value <0.01, *** p-value<0.001).')
```

>>>>

```{r GWMH1a}
GWM <- L %>%
  t() %>%
  data.frame() %>%
  mutate(SpCode = row.names(.)) %>%
  left_join(Q) %>%
  select(-SpCode) %>%
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>%
  group_by(strata, community) %>%
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# nQ <- array(rep(as.matrix(Q), n),
#             c(dim(Q), n),
#             list(row.names(Q), names(Q), 1:n))
# nQ <- array(apply(nQ, 3, function(x){
#   x[,'strata'] <- sample(x[,'strata'])
#   return(x)}), c(dim(Q), n),
#   list(row.names(Q), names(Q), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('L', 'nQ'))
# nGWM <- parApply(cl, nQ, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   L %>%
#     t() %>%
#     data.frame() %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(data.frame(x)) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     group_by(strata, community) %>%
#     mutate_each(funs(as.character), -abundance) %>%
#     mutate_each(funs(as.numeric), -abundance) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# })
# stopCluster(cl)
# nGWM <- array(unlist(lapply(nGWM, function(x) as.matrix(x[3:9]))),
#               c(dim(GWM[3:9]), n),
#               list(row.names(GWM), names(GWM[3:9]), 1:n))
# rm(cl, nQ)
# save(nGWM, file = file.path(path, 'nGWM_NM1.Rdata'))
load(file.path(path, 'nGWM_NM1.Rdata'))
GWM_pval <- GWM
GWM_pval[3:9] <- apply(
  array(c(as.matrix(GWM[3:9]), nGWM), c(dim(GWM[3:9]), n+1)), 
  1:2, function(x) rank(x)[1]/(n+1))
GWM_pval %>% 
  select(-community, -LES, -WES) %>% 
  group_by(strata) %>% 
  mutate_all(function(x) findInterval(x, c(0.05, 0.95)) == 1) %>% 
  summarise_all(function(x) sum(x, na.rm = T)/length(x)*100) %>% 
  kable(caption = 'Percentage of community significantly (p-value<0.05) different from null expectations with null model NM1 for each trait of GWMs, for canopy (C) and understorey (U) guilds, in abundance. See table \\@ref(tab:Traits) for abbreviations.')
```

@@

```{r GWVH1b}
GWV <- L %>%
  t() %>%
  data.frame() %>%
  filter(sum(.) > 2) %>%
  mutate(SpCode = row.names(.)) %>%
  left_join(Q) %>%
  select(-SpCode) %>%
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>%
  melt(id.vars = c('strata', 'community', 'abundance'),
       variable.name = 'trait', value.name = 'trait_value') %>%
  left_join(melt(GWM, id.vars = c('strata', 'community'),
                 variable.name = 'trait', value.name = 'GWM')) %>%
  group_by(strata, community, trait) %>%
  mutate(GWV = (trait_value - GWM)^2) %>%
  select(-trait_value, -GWM) %>%
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>%
  dcast(strata + community ~ trait)
# nL <- array(replicate(n, t(apply(L, 1, function(x){
#   x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "C"), "SpCode"]][x[Q[which(Q$strata == "C"), "SpCode"]] != 0])
#   x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0] <- sample(x[Q[which(Q$strata == "U"), "SpCode"]][x[Q[which(Q$strata == "U"), "SpCode"]] != 0])
#   return(x)
#   }))), c(dim(L), n), list(row.names(L), names(L), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('nL', 'Q', 'GWM'))
# nGWV <- parApply(cl, nL, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   x %>%
#     t() %>%
#     data.frame() %>%
#     filter(sum(.) > 2) %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(Q) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     melt(id.vars = c('strata', 'community', 'abundance'),
#          variable.name = 'trait', value.name = 'trait_value') %>%
#     left_join(melt(GWM, id.vars = c('strata', 'community'),
#                    variable.name = 'trait', value.name = 'GWM')) %>%
#     group_by(strata, community, trait) %>%
#     mutate(GWV = (trait_value - GWM)^2) %>%
#     select(-trait_value, -GWM) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>%
#     dcast(strata + community ~ trait)
# })
# stopCluster(cl)
# nGWV <- array(unlist(lapply(nGWV, function(x) as.matrix(x[3:9]))),
#               c(dim(GWV[3:9]), n),
#               list(row.names(GWV), names(GWV[3:9]), 1:n))
# rm(cl, nL)
# save(nGWV, file = file.path(path, 'nGWV_NM3.Rdata'))
load(file.path(path, 'nGWV_NM3.Rdata'))
GWV_pval <- GWV
GWV_pval[3:9] <- apply(
  array(c(as.matrix(GWV[3:9]), nGWV), c(dim(GWV[3:9]), n+1)), 
  1:2, function(x) rank(x)[1]/(n+1))
GWV_pval %>% 
  select(-community, -LES, -WES) %>% 
  group_by(strata) %>% 
  mutate_all(function(x) abs(x) > 0.95) %>% 
  summarise_all(function(x) sum(x, na.rm = T)/length(x)*100) %>% 
  kable(caption = 'Percentage of community significantly (p-value<0.05) different from null expectations with null model NM3 for each trait of GWVs, for canopy (C) and understorey (U) guilds, in abundance. See table \\@ref(tab:Traits) for abbreviations.')
```

@@

```{r GWMH2a}
GWM <- L %>% 
  t() %>% 
  data.frame() %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  group_by(strata, community) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# nQ <- array(rep(as.matrix(Q), n),
#             c(dim(Q), n),
#             list(row.names(Q), names(Q), 1:n))
# nQ <- array(apply(nQ, 3, function(x){
#   x[which(x[,"strata"] == "C"),'SpCode'] <- sample(x[which(x[,"strata"] == "C"),'SpCode'])
#   x[which(x[,"strata"] == "U"),'SpCode'] <- sample(x[which(x[,"strata"] == "U"),'SpCode'])
#   return(x)
#   }), c(dim(Q), n), list(row.names(Q), names(Q), 1:n))
# cl <- makeCluster(cores)
# clusterExport(cl, list('L', 'nQ'))
# nGWM <- parApply(cl, nQ, 3, function(x){
#   library(dplyr)
#   library(reshape2)
#   L %>%
#     t() %>%
#     data.frame() %>%
#     mutate(SpCode = row.names(.)) %>%
#     left_join(data.frame(x)) %>%
#     select(-SpCode) %>%
#     melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
#          variable.name = 'community', value.name = 'abundance') %>%
#     group_by(strata, community) %>%
#     mutate_each(funs(as.character), -abundance) %>%
#     mutate_each(funs(as.numeric), -abundance) %>%
#     summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance)
# })
# stopCluster(cl)
# nGWM <- array(unlist(lapply(nGWM, function(x) as.matrix(x[3:9]))),
#               c(dim(GWM[3:9]), n),
#               list(row.names(GWM), names(GWM[3:9]), 1:n))
# rm(cl, nQ)
# save(nGWM, file = file.path(path, 'nGWM_NM2.Rdata'))
load(file.path(path, 'nGWM_NM2.Rdata'))
GWM_ses <- GWM
GWM_ses[3:9] <- (GWM[3:9] - apply(nGWM, 1:2, mean, na.rm = T))/apply(nGWM, 1:2, sd, na.rm = T)
GWM_ses %>% 
  melt(id.vars = c('strata', 'community')) %>% 
  rename(trait = variable) %>% 
  rename(SES = value) %>% 
  left_join(R) %>%
  select(-community) %>% 
  group_by(strata, trait) %>% 
  do(tidy(step(lm(SES ~ Slope + Curvature + Wetness + SW + Canopy + BA, .), 
          direction = 'both', trace = 0))) %>% 
  group_by(strata, trait, term) %>%
  transmute(value = paste(format(estimate, scientific = T, digits = 2, trim = T), 
                          stars(p.value, ns = '   '))) %>% 
  dcast(strata + trait ~ term) %>% 
  select(strata, trait, Slope, Curvature, Wetness, SW, Canopy, BA) %>% 
  mutate_each(funs(replace(., is.na(.), ' '))) %>% 
  filter(trait != 'LES') %>% 
  filter(trait != 'WES') %>%
  bold() %>% 
  kable(caption = 'Linear models of the standardized effect size (SES) with null model NM2 for each trait of GWMs, for canopy (C) and understorey (U) guilds, in abundance. We performed stepwise selection of the predictors including slope, curvature, wetness southwesterness (SW), canopy height (Canopy) and basal area (BA), and only the selected predictors are shown. See table \\@ref(tab:Traits) for abbreviations. Bold and number of asterisk indicates the significance threshold ( * p-value<0.05, ** p-value <0.01, *** p-value<0.001).')
```

@@

```{r GWVH2b}
GWV <- L %>% 
  t() %>% 
  data.frame() %>% 
  filter(sum(.) > 2) %>% 
  mutate(SpCode = row.names(.)) %>% 
  left_join(Q) %>% 
  select(-SpCode) %>% 
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>% 
  melt(id.vars = c('strata', 'community', 'abundance'),
       variable.name = 'trait', value.name = 'trait_value') %>% 
  left_join(melt(GWM, id.vars = c('strata', 'community'),
                 variable.name = 'trait', value.name = 'GWM')) %>% 
  group_by(strata, community, trait) %>% 
  mutate(GWV = (trait_value - GWM)^2) %>% 
  select(-trait_value, -GWM) %>% 
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  dcast(strata + community ~ trait)
load(file.path(path, 'nGWV_NM3.Rdata'))
GWV_ses <- GWV
GWV_ses[3:9] <- (GWV[3:9] - apply(nGWV, 1:2, mean, na.rm = T))/apply(nGWV, 1:2, sd, na.rm = T)
load(file.path(path, 'GWV_NM3_ses.Rdata'))
GWV_ses %>% 
  melt(id.vars = c('strata', 'community')) %>% 
  rename(trait = variable) %>% 
  rename(SES = value) %>% 
  left_join(R) %>%
  select(-community) %>% 
  group_by(strata, trait) %>% 
  do(tidy(step(lm(SES ~ Slope + Curvature + Wetness + SW + Canopy + BA, .), 
          direction = 'both', trace = 0))) %>% 
  group_by(strata, trait, term) %>%
  transmute(value = paste(format(estimate, scientific = T, digits = 2, trim = T), 
                          stars(p.value, ns = '   '))) %>% 
  dcast(strata + trait ~ term) %>% 
  {if(!("Slope" %in% names(.))) mutate(., Slope = NA)} %>% 
  select(strata, trait, Slope, Curvature, Wetness, SW, Canopy, BA) %>% 
  mutate_each(funs(replace(., is.na(.), ' '))) %>% 
  filter(trait != 'LES') %>% 
  filter(trait != 'WES') %>%
  bold() %>% 
  kable(caption = 'Linear models of the standardized effect sizes (SES) with null model NM3 of GWV for canopy (C) and understorey (U) guilds. We performed stepwise selection of the predictors including slope, curvature, wetness southwesterness (SW), canopy height (Canopy) and basal area (BA), and only the selected predictors are shown. See table \\@ref(tab:Traits) for abbreviations. Bold and  number of asterisk indicates the significance threshold ( * p-value<0.05, ** p-value <0.01, *** p-value<0.001).')
```
